%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.5 in} % Text width of the document

\usepackage{url}
\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Mingyuan BAI} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{The University of Sydney Business School, The University of Sydney} % Your address
\moveleft.5\hoffset\centerline{H70, The University of Sydney, Darlington, NSW, Australia}
\moveleft.5\hoffset\centerline{(+86) 13482318406}
\moveleft.5\hoffset\centerline{yvonne.mingyuanbai@gmail.com}
\moveleft.5\hoffset\centerline{\url{https://www.mymingyuanbai.com}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
% \section{Objective}  

% To be admitted as a research intern in Alibaba Group in 2019
% %as a tutor to QBUS6850 in Semester 2 2019
% %the opportunity to be admitted to the Master of Science in Mathematical Science program at Oxford University from 2018

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------
% \section{Objective}
% To be accepted by Akuna Capital in 2022
\section{Education}
{\sl Doctor of Philosophy (Business Analytics)} \hfill March 2018 - Present\\
The University of Sydney
\begin{itemize}
    \item Thesis topics: multi-dimensional data analysis, tensor decomposition, dimensionality reduction deep learning
    \item Thesis applications: share price prediction, graphical relational data forecast (market leader detection and forecast)
\end{itemize}

{\sl Bachelor of Commerce (First Class Honours)} \hfill March 2017 - December 2017\\
The University of Sydney
\begin{itemize}
\item Major: Business Analytics
\item Thesis topics: tensorial neural networks, tensorial recurrent neural networks and optimization on Riemannian manifolds
\end{itemize}


{\sl Bachelor of Commerce} \hfill March 2014 - December 2016\\
The University of Sydney
\begin{itemize}
\item Majors: Accounting and Quantitative Business Analysis
\end{itemize} 

\section{Programming Skills} 

%{\sl Programming Languages:} 
MATLAB, Python (PyTorch, TensorFlow, Keras), Bash (Unix shell), LaTeX and SAS; \\

% \section{Language Skills}
% Basic Russian, proficient English and native speaker level Chinese in writing, listening and speaking
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Awards}
St Paul's College academic bursary, 2019-Present

Business school research scholarship, the University of Sydney, 2018-Present

Best student paper award finalist, the 24th International Conference On Neural Information Processing, 2017

First-class honours in the University of Sydney, 2017

Ranked 2nd for the thesis ``Tensorial Neural Networks for
Longitudinal Network Data Analysis" in 34 students for the Honours program, 2017

\section{Experiences}
% {\sl Teaching Assistant} \hfill March 2018 - Present\\
% {The University of Sydney Business School, Sydney, Australia}
% \begin{itemize}
% % \item Deliver the tutorials on statistics, machine learning and econometrics.
% \end{itemize}
{\sl Tutor for QBUS6850} \hfill July 2019 - December 2019 \\
{The University of Sydney Business School, Sydney, Australia}
\begin{itemize}
\item Deliver tutorials on machine learning and deep learning in Python (Tensorflow and Keras).
\end{itemize}

{\sl Tutor for QBUS6840} \hfill March 2019 - June 2019 \\
{The University of Sydney Business School, Sydney, Australia}
\begin{itemize}
\item Deliver tutorials on forecasting methods in statistics, machine learning and econometrics in Python.
\end{itemize}

{\sl Summer Intern} \hfill September 2016 - February 2017 \\
{Elite International Investment, Sydney, Australia}
\begin{itemize}
\item Conduct research on real estate properties in the Greater Sydney suburbs, including political, economic and social cultural perspectives for qualitative analysis and land prices forecasting for quantitative analysis.
\item Assist decision making for land purchase by the company.
\item Build the database of real estate information in the Greater Sydney Inner West, Northwest and Southwest suburbs.
\item Complete the report of all Greater Sydney suburbs real estate investment analysis with the team, in charge of Inner West, Northwest and Southwest suburbs.
\end{itemize}

{\sl Lending and Operations Intern} \hfill December 2015 - February 2016 \\
{Australia and New Zealand Banking Group, Shanghai, China}
\begin{itemize}
\item Conduct lend reconciliation.
\item Update the lending history from the credit reports. Identify the clients at risk and report to the lending operations department manager.
\item Check the bank confirmation with the team and send the confirmed version to the auditor teams.
\end{itemize}

{\sl Assistant Duty Manager} \hfill December 2014 - February 2015 \\
{Bank of China, Changchun, Jilin, China}
\begin{itemize}
\item Assist the daily client service.
\item Activate the bank cards for clients.
\end{itemize}

\section{Services}
% {\sl Teaching Assistant} \hfill March 2018 - Present\\
% {The University of Sydney Business School, Sydney, Australia}
% \begin{itemize}
% % \item Deliver the tutorials on statistics, machine learning and econometrics.
% \end{itemize}
{\sl Reviewer} \hfill March 2019 - Present \\
{IEEE Transactions on Neural Networks and Learning Systems}
\begin{itemize}
\item Review journal articles for the rank A$^*$ journal in data science and computer science.
\end{itemize}
%\begin{itemize}
% \item Deliver the tutorials on statistics, machine learning and econometrics.
%\end{itemize}
% {\sl Tutor for BUSS1020}\\
% {Helper for QBUS5001 and QBUS5002} \hfill March 2018 - June 2018 \\
% {The University of Sydney Business School, Sydney, Australia}

\newpage
\section{Publications}
\textbf{Mingyuan Bai}, Jie Chen, Qibin Zhao, Chao Li, Junping Zhang and Junbin Gao, ``Tensor Neural Controlled Differential Equations'', submitted to IEEE International Conference on Acoustics, Speech and Signal Processing, 2022.

Jie Chen, Shouzhen Chen, \textbf{Mingyuan Bai}, Jian Pu, Junping Zhang and Junbin Gao, ``Graph Decoupling Attention Markov Networks for Semi-supervised Graph Node Classification'', submitted to IEEE Transactions on Neural Networks and Learning Systems, 2022. (Minor revision)

\textbf{Mingyuan Bai}, Qibin Zhao and Junbin Gao, ``Tensorial Time Series Prediction via Tensor Neural Ordinary Differential Equations'', to appear in International Joint Conference on Neural Networks (IJCNN), 2021. (Applications: stock market price forecasting, corporate relation prediction and international relation forecast)

Di Xu$^*$, \textbf{Mingyuan Bai}$^*$, Tianhang Long and Junbin Gao, ``LSTM-Assisted Evolutionary Self-Expressive Subspace Clustering'', International Journal of Machine Learning and Cybernetics, 2021. ($^*$: equally contributed; applications: real-time motion segmentation, ocean water mass clustering, social science)

\textbf{Mingyuan Bai}, Boris S.T. Choy, Xin Song and Junbin Gao, ``Tensor-Train Parameterization for Ultra Dimensionality Reduction'', IEEE International Conference on Big Knowledge (ICBK), 2019. (Applications: facial recognition and remote sensing; working further applications: forecast of stock prices, market leader detection and forecast)

\textbf{Mingyuan Bai}, Boyan Zhang and Junbin Gao, ``Tensorial Neural Networks and Its Application in Longitudinal Network Data Analysis", the 24th International Conference on Neural Information Processing (ICONIP), 2017. (Best student paper award finalist)

\textbf{Mingyuan Bai}, Boyan Zhang and Junbin Gao, ``Tensorial Recurrent Neural Networks for Longitudinal Data Analysis", arXiv:1708.00185.

\textbf{Mingyuan Bai}, Boyan Zhang and Junbin Gao. ``Recurrent Neural Networks for Multimodal Time Series Data Analysis: An Overview", to appear in Multimodal Analytics for Next Generation Big Data Technologies and Applications.
\end{resume}
\end{document}
