%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.5 in} % Text width of the document

\usepackage{url}
\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Jane DOE} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{School of XXX, The University of Wonderland} % Your address
\moveleft.5\hoffset\centerline{H70, The University of Wonderland, Darlington, NSW, Australia}
\moveleft.5\hoffset\centerline{(+61) 000-000-000}
\moveleft.5\hoffset\centerline{jane.doe@sydney.edu.au}
\moveleft.5\hoffset\centerline{\url{https://www.janedoe.com}}

%----------------------------------------------------------------------------------------

\begin{resume}
\section{Education}
{\sl Doctor of Philosophy (\textit{Research Area})} \hfill \textit{Month} \textit{Year} - Present\\
The University of Wonderland
\begin{itemize}
    \item Thesis topics: multi-dimensional time series analysis, diffusion models, machine learning
    \item Thesis applications: share price prediction, video generation
\end{itemize}

{\sl Bachelor of XXX (XXX Class Honours)} \hfill \textit{Month} \textit{Year} - \textit{Month} \textit{Year}\\
The University of Wonderland
\begin{itemize}
\item Major: XXX
\item Thesis topics: time series analysis, machine learning
\end{itemize}


{\sl Bachelor of XXX} \hfill \textit{Month} \textit{Year} - \textit{Month} \textit{Year}\\
The University of Wonderland
\begin{itemize}
\item Majors: XXX
\end{itemize} 

\section{Programming Skills} 
MATLAB, Python (PyTorch, TensorFlow, Keras), Bash (Unix shell), LaTeX and SAS; \\

% \section{Language Skills}
% Basic Russian, proficient English and native speaker level Chinese in writing, listening and speaking
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Awards}
XXX Fellowship, Year-Present

XXX Award, Year

First-class honours in the University of Wonderland, Year

\section{Experiences}
{\sl Tutor for STATSXXXX} \hfill Month Year - Month Year \\
{School of XXX, The University of Wonderland, City, Country}
\begin{itemize}
\item Deliver tutorials on machine learning and deep learning in Python (Tensorflow and Keras) in classes of $33$. Receive top $10\%$ ratings on tutoring.
\end{itemize}

\section{Services}
{\sl Reviewer} \hfill Month Year - Present \\
{IEEE Transactions on XXX}
\begin{itemize}
\item Review journal articles for the rank A$^*$ journal in data science and computer science.
\end{itemize}

\newpage
\section{Publications}
\textbf{Jane Doe}, John Doe and Johnny Doe, ``Title of Your Paper'', submitted to the 17th IEEE Conference on XXX, Year.

John Doe and \textbf{Jane Doe}, ``Title of Your Paper'', submitted to IEEE Transactions on XXX, Year. (Minor revision)

\textbf{Jane Doe}, John Doe and Johnny Doe, ``Title of Your Paper'', to appear in the 16th IEEE Conference on XXX, Year.

Jenny Doe$^*$, \textbf{Jane Doe}$^*$, John Doe and Johnny Doe, ``Title of Your Paper'', ACM Conference on XXX, Year. ($^*$: equally contributed)

\textbf{Jane Doe} and John Doe, ``Title of Your Paper'', the 15th IEEE Conference on XXX, Year.

\textbf{Jane Doe}, John Doe and Johnny Doe, ``Title of Your Paper", the 14th International Conference on XXX, Year. (Best student paper award)

\textbf{Jane Doe}, John Doe and Johnny Doe, ``Title of Your Paper", arXiv:XXXX.XXXXX.
\end{resume}
\end{document}
